---
title: "Challenge-6"
author: "Niki"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

**Solutions:**

```{r, eval=T,echo=TRUE}
# Enter code here

i <- 10
while (0 <= i & i <= 10) { Sys.sleep(1)
cat(" ",i,"...","\n" )
i <- i - 1 }

cat("Blast off!!!")


```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Enter code here

word <- "chicken nugget"

reversed <- ""
index <- nchar(word)

while (index > 0) {
  reversed <- paste(reversed, substr(word, index, index), sep = "")
  index <- index - 1
}

cat("Reversed word:", reversed, "\n")


```
<br>
